---
title: "Untitled"
author: "Tyler Lawrence"
date: "2023-11-27"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
```

## Billionaire Data:

This is today I will be using some billionaire data from this year I found on Kaggle, at <https://www.kaggle.com/datasets/nelgiriyewithana/billionaires-statistics-dataset>.

## Questions to answer:
- What is the difference between the genders when it comes to wealth?
- How does wealth scale with age?
- Which industries make the most money?

## Some code for you

billionares <- read.csv("Billionaires Statistics Dataset.csv")
usBills <- billionares %>% filter(country == "United States" & rank <= 500) %>% mutate(usRank = as.integer(rank(-finalWorth))) %>% select(usRank, finalWorth, category, personName, country, source, status, gender, birthYear)

## Let's start with a comparison of the representation of genders.
```{r, echo=FALSE}
billionares <- read.csv("Billionaires Statistics Dataset.csv")
usBills <- billionares %>% filter(country == "United States" & rank <= 500) %>% mutate(usRank = as.integer(rank(-finalWorth))) %>% select(usRank, finalWorth, category, personName, country, source, status, gender, birthYear)
ggplot(usBills, aes(gender, fill = gender)) + geom_bar()

```
## Not looking good!
As you can see, the distribution of wealth between the sexes is a little uneven!

But that's just the amount of people, how much does the average female billionaire make compared to the average male billionaire?

## Mean of wealth of the males and females:
```{r}
usBills %>% group_by(gender) %>% summarize(mean(finalWorth))
```

Not as bad as it could be, but not very good either.

## Here's the density by rank of the sexes
```{r}
ggplot(usBills, aes(fill = gender, x = usRank)) + geom_density(alpha = .5)

```

## Now that I've shown the sexism in the American Capitalist system, how about we show how age affects wealth?
```{r}
ggplot(usBills, aes(birthYear)) + geom_histogram()

```

That's not great either! 

## Now how do certain industries compare to others?
```{r}
usBills %>% group_by(category) %>% summarize(mean(finalWorth)) %>% ggplot(aes(category, `mean(finalWorth)`)) + geom_col() + coord_flip()

```

As we can see, the automotive industry dominates against all other industries, however, this might be mostly because of Elon Musk, who is listed as only automotive.

## Thank you for listening!